`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-01-10 inst/manuscript/manuscript.rmd
Make pandoc understand "em"-dashes;

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: no
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
csl: biomed-central.csl
bibliography: flippant.bib
---

>>>>

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: no
    pandoc_args: ["--smart"]
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
csl: biomed-central.csl
bibliography: flippant.bib
---
